Conjure: Summoning Proxies from Unused Address Space

### 2019-09-28 paper/paper.tex
Small spell fixes

Finally, we assume the censor can replay or preplay any connections that it
suspects involve phantom hosts (or their registration) in an attempt to confirm.
However, the censor wishes to avoid disrupting any connections before it
knows for certain they are from \scheme clients, lest they disrupt legitimate
connections. This means that injecting false data or corrupting TLS sessions is
outside the scope of the censor, but that the censor can send non-disruptive
probes (such as stale TCP acknowledgements) that would normally
be ignored. We emphasize that TapDance is observable by censors that can send
TCP packets in suspected connections, but that our protocol is robust against
this class of censor.

@@

\subsection{Registration}
\label{sec:registration}
We use a form of Refraction Networking similar to Tapdance to register directly with
the station, though \scheme registration is significantly simpler and more difficult
to detect than vanilla Tapdance. This is because registration flows are unidirectional; 
a client communicates their intent to register to the station without any 
response from the station itself. This makes registration flows very difficult to detect as they 
can be sent to any site hosted behind the ISP, and display no evidence of proxy behavior.

@@

A registration connection is sent to a \textbf{registration decoy}: any site that 
supports TLS behind the ISP relative to the client. The client completes the handshake,
and sends a normal HTTPS request that embeds a ciphertext tag in the payload. 
\scheme leverages the same steganographic technique as Tapdance to encode the 
ciphertext~\cite[\S3]{tapdance14}, however we send a complete request allowing the
registration decoy to respond or close the connection. The tag is encrypted such 
that it is only visible to the station. The \scheme station passively observes
tagged flows obviating the need to mimic the decoy. In addition, more potential 
decoys can be used in comparison to TapDance, as there is no need to exclude decoys that 
have timeouts or TCP windows unfavorable for keeping connections open. In our 
deployment, this results in a modest increase of 25\% more decoys that could be 
used than in TapDance.

>>>>

Finally, we assume the censor can replay or preplay any connections that it
suspects involve phantom hosts (or their registration) in an attempt to confirm.
However, the censor wishes to avoid disrupting any connections before it
knows for certain they are from \scheme clients, lest they disrupt legitimate
connections. This means that injecting false data or corrupting TLS sessions is
outside the scope of the censor, but that the censor can send non-disruptive
probes (such as stale TCP acknowledgments) that would normally
be ignored. We emphasize that TapDance is observable by censors that can send
TCP packets in suspected connections, but that our protocol is robust against
this class of censor.

@@

\subsection{Registration}
\label{sec:registration}
We use a form of Refraction Networking similar to TapDance to register directly with
the station, though \scheme registration is significantly simpler and more difficult
to detect than vanilla TapDance. This is because registration flows are unidirectional; 
a client communicates their intent to register to the station without any 
response from the station itself. This makes registration flows very difficult to detect as they 
can be sent to any site hosted behind the ISP, and display no evidence of proxy behavior.

@@

A registration connection is sent to a \textbf{registration decoy}: any site that 
supports TLS behind the ISP relative to the client. The client completes the handshake,
and sends a normal HTTPS request that embeds a ciphertext tag in the payload. 
\scheme leverages the same steganographic technique as TapDance to encode the 
ciphertext~\cite[\S3]{tapdance14}, however we send a complete request allowing the
registration decoy to respond or close the connection. The tag is encrypted such 
that it is only visible to the station. The \scheme station passively observes
tagged flows obviating the need to mimic the decoy. In addition, more potential 
decoys can be used in comparison to TapDance, as there is no need to exclude decoys that 
have timeouts or TCP windows unfavorable for keeping connections open. In our 
deployment, this results in a modest increase of 25\% more decoys that could be 
used than in TapDance.
